Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-15 doc/GMP2015/s08_pinnedline.tex
Modified definition of trivial graph

Collagen is an important protein material in biological tissues with highly elastic mechanical property. 
Cellulose is the most important constituent of the cell wall of plants (see Figure~\ref{fig:cellulose}). 
Both of these substances consist of a large number microfibrils,
%fibril itself straight?
%Each fibril is attached to some fixed larger organelle/membrane at one spot (typically on the boundary).
%It is additionally 
each of which is cross-linked at 2 places with some two other fibrils, 
where the cross-linking is like an incidence constraint that 
the two crosslinked fibrils can slide with each other (see Figure~\ref{fig:cross-linking}(a). ).

@@

%TODO system? problem?
\begin{definition} [2-Dimensional Pinned Line Incidence Graph] \label{prob:pinned_subspace}
A simple graph $G=(V,E)$ is a 2-dimensional pinned line incidence graph, 
if there is  a  set $X$ of $|E|$ pins with fixed positions in $\mathbb{R}^2$.
such that 
 every edge $e \in E$ corresponds to a pin $x \in X$ where $e$ is constrained to lie on a line passing through $x$.
%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$

@@

\item 
\todo{We just define the trivial graph/DR-plan leaf for 2-dimensional pinned line incidence graphs to be a single vertex.  }

@@

\todo{All Lemmas before Lemma 8 are proved with respect to general constraint systems,
and they go through for 2-dimensional pinned line incidence as well. }
Now we  show that Lemma 8 also holds for 2-dimensional pinned line incidence graphs.

>>>>

Collagen is an important protein material in biological tissues with highly elastic mechanical property. 
Cellulose is the most important constituent of the cell wall of plants (see Figure~\ref{fig:cellulose}). 
Both of these substances consist of a large number microfibrils,
%fibril itself straight?
%Each fibril is attached to some fixed larger organelle/membrane at one spot (typically on the boundary).
%It is additionally 
each of which is cross-linked at 2 places with some two other fibrils, 
where the cross-linking is like an incidence constraint that 
the two crosslinked fibrils can slide with each other (see Figure~\ref{fig:cross-linking}(a)).

@@

%TODO system? problem?
\begin{definition} [2-Dimensional Pinned Line Incidence Graph] \label{prob:pinned_subspace}
A simple graph $G=(V,E)$ is a 2-dimensional pinned line incidence graph, 
if there is  a  set $X$ of $|E|$ pins with fixed positions in $\mathbb{R}^2$,
such that  every edge $e \in E$ corresponds to a pin $x \in X$ where $e$ is constrained to lie on a line passing through $x$.
%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$

@@

\item 
\todo{We just define the %trivial graph/
DR-plan leaves for 2-dimensional pinned line incidence graphs to be single vertices...  }

@@

\todo{All Lemmas before Lemma 8 are proved with respect to general constraint systems,
and they go through for 2-dimensional pinned line incidence as well (without trivial graph??). }

Now we  show that Lemma 8 also holds for 2-dimensional pinned line incidence graphs.
